---
title: "In Class Lab - DIY Functions"
author: "Dr. Shoemaker"
date: "DATA 2401"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Write your own function that takes the temperature in Fahrenheit as an argument and returns the Celcius equivalent. 

```{R}
temp_convert <- function(fahrenheit) {
  celsius <- (fahrenheit - 32) * (5/9)
   return(celsius)
}
temp_convert(100)
```

2. Expand that function so that it takes a temperature in Fahrenheit and a distance in feet and returns **both** the temperature in Celcius and the distance in meters (you'll likely need to remember the `c()` function!)


```{r}
temp_convert <- function(fahrenheit, feet) {
  celsius <- (fahrenheit - 32) * (5/9)
  meters <- feet * 0.3048
   return(c(celsius, meters))
}
temp_convert(100,89)
temp_convert(32,6)
```


3. Write a function that prints out a statement of whether the number passed as an argument is positive, negative or 0. 

```{R}
decide = function(int) {
  if (int > 0) {
  print ("integer is positive")
 } else if (int == 0) {
  print ("integer is equal to 0")
 } else {
  print ("integer is negative")
 }
}
decide(6)
decide(9)
decide(-9)
decide(0)
```

4. Write a function that returns the absolute value of the number passed as an argument.
   + Don't use `abs()`. Use the flow from problem 1 and multiply by negative one as necessary. 
   
```{r}
absolute <- function(int) {
  if (int >= 0) {
    print(int)
  } else {
    convert = int * -1
    print(convert)
  }
}
absolute(-5)
absolute(-11)
```

5. Hard mode: add an error check to that function that prints out the string "Please pass a numerical value to this function" if the user passes the function a string. 
   + There are functions that check and return T/F: `is.numeric()` or `is.character()` would be relevant here
   
```{r}
data_type = function(input) {
  if (is.character(input)) {
    statement =  "Please pass a numerical value to this function"
  } else if (is.numeric(input)) {
    statement <- ("good job")
  }
  statement
}
data_type("que paso")
data_type(7111107)

```
   
   






```

